---
title: "DATA 608 - HOMEWORK 1"
author: "Fan Xu"
date: "2/14/2021"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_collapsed: yes
    toc_float: yes
  html_notebook: default
  rmdformats::readthedown:
    code_folding: hide
    df_print: paged
    highlight: tango
    number_sections: yes
    smooth_scroll: yes
    theme: united
    toc_collapsed: yes
    toc_depth: 5
    toc_float: yes
  pdf_document:
    extra_dependencies:
    - geometry
    - multicol
    - multirow
  word_document:
    toc: yes
    toc_depth: '5'
theme: lumen
number_sections: yes
toc_depth: 3
---

```{r load library, message=FALSE, warning=FALSE}
library(tidyverse)
```

**Principles of Data Visualization and Introduction to ggplot2**

I have provided you with data about the 5,000 fastest growing companies in the US, as compiled by Inc. magazine. lets read this in:

```{r}

inc <- read.csv("https://raw.githubusercontent.com/charleyferrari/CUNY_DATA_608/master/module1/Data/inc5000_data.csv", header= TRUE)

```

And lets preview this data:

```{r}

head(inc)

```
```{r}

summary(inc)

```

Think a bit on what these summaries mean. Use the space below to add some more relevant non-visual exploratory information you think helps you understand this data:

```{r}

# Insert your code here, create more chunks as necessary

glimpse(inc)
```

## Question 1

Create a graph that shows the distribution of companies in the dataset by State (ie how many are in each state). There are a lot of States, so consider which axis you should use. This visualization is ultimately going to be consumed on a 'portrait' oriented screen (ie taller than wide), which should further guide your layout choices.

```{r}

# Answer Question 1 here
inc %>%
  group_by(State) %>%
  tally(n='Count') %>%
  ggplot(aes(x=fct_reorder(State, Count), y=Count)) +
  geom_bar(stat='identity', fill='deeppink4') +
  coord_flip() +
  ggtitle('Histogram: Number of Companies by State') +
  xlab('State') +
  theme(panel.background = element_rect(fill='transparent'),
        axis.text.y = element_text(size = 5)) +
  geom_text(aes(label = Count),size = 2, hjust= -0.5, vjust = 0.3)

```

## Quesiton 2

Lets dig in on the state with the 3rd most companies in the data set. Imagine you work for the state and are interested in how many people are employed by companies in different industries. Create a plot that shows the average and/or median employment by industry for companies in this state (only use cases with full data, use R's `complete.cases()` function.) In addition to this, your graph should show how variable the ranges are, and you should deal with outliers.

```{r message=FALSE, warning=FALSE}

# Answer Question 2 here
inc %>%
  filter(complete.cases(.), State=='NY') %>%
  group_by(Industry) %>%
  ggplot(aes(x=reorder(Industry, Employees, mean), y=Employees)) +
  #outliner removed from boxplot
  geom_boxplot(fill = 'deeppink4', outlier.shape = NA) +
  scale_y_continuous(limits=c(0,1000)) +
  stat_summary(fun=mean, geom = 'point', color='lightgrey') +
  coord_flip() +
  ggtitle('Numbers of Employee by Industry for Companies in NY') +
  xlab('Industry') +
  ylab('Employees (Points Stand for Average)') +
  theme(panel.background = element_rect(fill='transparent')) 



```




## Question 3

Now imagine you work for an investor and want to see which industries generate the most revenue per employee. Create a chart that makes this information clear. Once again, the distribution per industry should be shown.




```{r message=FALSE, warning=FALSE}

# Answer Question 3 here
inc %>%
  filter(complete.cases(.)) %>%
  mutate(Revenue_Per_Employee = Revenue/Employees) %>%
  ggplot(aes(x=reorder(Industry, Revenue_Per_Employee, mean), y=Revenue_Per_Employee)) +
  #outliner removed from boxplot
  geom_boxplot(fill = 'deeppink4', outlier.shape = NA) +
  stat_summary(fun=mean, geom = 'point', color='lightgrey') +
  coord_flip() +
  ggtitle('Revenue per Employee by Industry for Companies in NY') +
  xlab('Industry') +
  ylab('Revenue per Employees (Points Stand for Mean Value)') +
  theme(panel.background = element_rect(fill='transparent')) +
  scale_y_continuous(limits=c(0,1500000))
```


